HumanCdGF_microbiota_predict_by_day

### 2016-09-30 code/HumanCdGF_microbiota_predict_by_day.Rmd
color cfu otu dependence by outcome

cfu_by_day_comm %>% 
  select(log_cfu, day, one_of(predictive_otus)) %>% 
  filter(!is.na(log_cfu)) %>% 
  gather('otu','abundance',contains('Otu')) %>% 
  full_join(predictive_taxa) %>% 
  ggplot(aes(x = abundance, y = log_cfu, color = factor(day))) + geom_point() + 
    facet_wrap(~ tax_label, scales = 'free_x') +
    labs( x = 'Relative Abundance', y = 'CFU (log10)')

@@

```{r fig.width=10, fig.height=10}
cfu_by_day_comm %>% 
  select(log_cfu, day, one_of(predictive_otus)) %>% 
  filter(!is.na(log_cfu)) %>% 
  gather('otu','abundance',contains('Otu')) %>% 
  full_join(predictive_taxa) %>% 
  ggplot(aes(x = log10(abundance), y = log_cfu, color = factor(day))) + geom_point() + 
    facet_wrap(~ tax_label, scales = 'free_x') +
    labs( x = 'Relative Abundance (log10)', y = 'CFU (log10)')

@@

```{r fig.width=10, fig.height=10}
meta_file %>% 
  select(day, log_cfu, mouse_id) %>% 
  full_join(day_0_otu_by_mouse) %>% 
  select(day, log_cfu, one_of(predictive_otus)) %>% 
  filter(!day == 0) %>% 
  gather('otu', 'abundance', contains('Otu')) %>% 
  filter(!is.na(abundance)) %>% 
  full_join(predictive_taxa) %>% 
  ggplot(aes(x = abundance, y = log_cfu, color = factor(day))) + geom_point() + 
    facet_wrap(~ tax_label, scales = 'free_x') +
    labs( x = 'Relative Abundance', y = 'CFU (log10)')

@@

```{r fig.width=10, fig.height=10}
meta_file %>% 
  select(day, log_cfu, mouse_id) %>% 
  full_join(day_0_otu_by_mouse) %>% 
  select(day, log_cfu, one_of(predictive_otus)) %>% 
  filter(!day == 0) %>% 
  gather('otu', 'abundance', contains('Otu')) %>% 
  filter(!is.na(abundance)) %>% 
  full_join(predictive_taxa) %>% 
  ggplot(aes(x = log10(abundance), y = log_cfu, color = factor(day))) + geom_point() + 
    facet_wrap(~ tax_label, scales = 'free_x') +
    labs( x = 'Relative Abundance (log10)', y = 'CFU (log10)')

>>>>

cfu_by_day <-
  meta_file %>% 
  filter(day %in% 1:10) %>% 
  select(sample_id, day, log_cfu, Early_Euth) %>% 
  left_join(rel_abund_shared_01) %>% 
  select(-sample_id, -one_of(cdiff_otu))

cfu_by_day %>% 
  select(log_cfu, day, one_of(predictive_otus), Early_Euth) %>% 
  filter(!is.na(log_cfu)) %>% 
  gather('otu','abundance',contains('Otu')) %>% 
  full_join(predictive_taxa) %>% 
  ggplot(aes(x = abundance, y = log_cfu, color = factor(Early_Euth))) + geom_point() + 
    facet_wrap(~ tax_label, scales = 'free_x') +
    labs( x = 'Relative Abundance', y = 'CFU (log10)')

@@

```{r fig.width=10, fig.height=10}
cfu_by_day %>% 
  select(log_cfu, day, one_of(predictive_otus), Early_Euth) %>% 
  filter(!is.na(log_cfu)) %>% 
  gather('otu','abundance',contains('Otu')) %>% 
  full_join(predictive_taxa) %>% 
  ggplot(aes(x = log10(abundance), y = log_cfu, color = factor(Early_Euth))) + geom_point() + 
    facet_wrap(~ tax_label, scales = 'free_x') +
    labs( x = 'Relative Abundance (log10)', y = 'CFU (log10)')

@@

```{r fig.width=10, fig.height=10}
meta_file %>% 
  select(day, log_cfu, mouse_id, Early_Euth) %>% 
  full_join(day_0_otu_by_mouse) %>% 
  select(day, log_cfu, one_of(predictive_otus), Early_Euth) %>% 
  filter(!day == 0) %>% 
  gather('otu', 'abundance', contains('Otu')) %>% 
  filter(!is.na(abundance)) %>% 
  full_join(predictive_taxa) %>% 
  ggplot(aes(x = abundance, y = log_cfu, color = factor(Early_Euth))) + geom_point() + 
    facet_wrap(~ tax_label, scales = 'free_x') +
    labs( x = 'Relative Abundance', y = 'CFU (log10)')

@@

```{r fig.width=10, fig.height=10}
meta_file %>% 
  select(day, log_cfu, mouse_id, Early_Euth) %>% 
  full_join(day_0_otu_by_mouse) %>% 
  select(day, log_cfu, one_of(predictive_otus), Early_Euth) %>% 
  filter(!day == 0) %>% 
  gather('otu', 'abundance', contains('Otu')) %>% 
  filter(!is.na(abundance)) %>% 
  full_join(predictive_taxa) %>% 
  ggplot(aes(x = log10(abundance), y = log_cfu, color = factor(Early_Euth))) + geom_point() + 
    facet_wrap(~ tax_label, scales = 'free_x') +
    labs( x = 'Relative Abundance (log10)', y = 'CFU (log10)')
